Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-10 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
corresponding data point in the other set. This immediate correlation allows not only for correlating
studies in fixed samples, but also studies of dynamics in live samples.

@@

Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
simultaneously and -- because fluorescence signals should be investigated, which were originated
from particles at or near to the surface of the cell -- it was important to keep the distance 
between the sample and the pipette constant. In that study the SSCM was used for investigating the 
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.

SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
\cite{Novak2014}.

>>>>

@@

As the SICM and SCM data sets are recorded simultaneously, all data points immediately have a
corresponding data point in the other set. This immediate correlation allows not only for correlating
studies in fixed samples (figure \ref{fig:sicm+scm}c), but also studies of dynamics in live samples 
(figure \ref{fig:sicm+scm}d).

To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
(figure \ref{fig:sicm+scm}d), for the investigating the uptake of fluorescent nanoparticles in 
immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.

%Anmerkung: Habe die folgenden Paragraphen versucht in oberen Text einzubauen und deshalb hier 
%auskommentiert.

%Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
%scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
%simultaneously and -- because fluorescence signals should be investigated, which were originated
%from particles at or near to the surface of the cell -- it was important to keep the distance 
%between the sample and the pipette constant. In that study the SSCM was used for investigating the 
%dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
%The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
%(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
%cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
%
%SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
%investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
%and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
%mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
%200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
%1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
%fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
%light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
%the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
%interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
%\cite{Novak2014}.
